SunPy - Python for Solar Physics

### 2014-01-30 3-4-Helioviewer.tex
Resize png image in Helioviewer

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helioviewer import HelioviewerClient
>>> hv = HelioviewerClient()
>>> hv.download_png('2099/01/01', 6,
...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
...                 "[SOHO,LASCO,C2,white-light,1,100]",
...                 x0=0, y0=0, width=768, height=768)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{helioviewer_overlay_example}
\end{center}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> filepath = hv.download_jp2('2012/07/05 00:30:00',
...                            observatory='SDO',
...                            instrument='HMI', detector='HMI', 
...                            measurement='continuum')
>>> from sunpy import map
>>> map.Map(filepath).submap([200,550],[-400,-200]).peek()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
\end{center}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy \texttt{Map} object.}
\label{code:downloadjp2}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helioviewer import HelioviewerClient
>>> hv = HelioviewerClient()
>>> hv.download_png('2099/01/01', 6,
...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
...                 "[SOHO,LASCO,C2,white-light,1,100]",
...                 x0=0, y0=0, width=768, height=768)
\end{minted}
\begin{center}
\includegraphics[width=0.6\columnwidth]{helioviewer_overlay_example}
\end{center}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> filepath = hv.download_jp2('2012/07/05 00:30:00',
...                            observatory='SDO',
...                            instrument='HMI', detector='HMI', 
...                            measurement='continuum')
>>> sunpy.map.Map(filepath).submap([200,550],[-400,-200]).peek()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
\end{center}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy \texttt{Map} object.}
\label{code:downloadjp2}
\end{listing}
